\begin{cvletter}
  % Introduction
  If loving charts is wrong, I don’t want to be right.
  I want to express my interest in your Graphics Reporter role, so that I may turn my passion for visual storytelling into a profession.
  More importantly, I will illustrate how I can help bridge the gap between The Washington Post and its mission to connect the public to the truth.

  % Who are you; and why it matters
  I am an experienced practitioner and data wrangler with a unique breadth of experience and capability for charts.
  During my Informatics undergraduate at the University of Iowa, I developed many of the skills you are seeking; including making maps, applying best practices within a student newsroom, and collaborating within a team of experts.
  After graduating I leveraged my experience into a research position with a professor, investigating fake news and bots on Twitter.
  Since publishing our findings, I have moved onto freelancing for the latest startup, where I have been for the last two years.

  % Why the company; what you can do
  However, that does not excite me nearly as much as what your graphics team is doing.
  I want to contribute to something greater than myself and your commitment to unbiased journalism is exactly what I am looking for.
  Unfortunately, misinformation has only gained relevance as digital manipulation becomes more commonplace.
  Recent examples include the Twitter hack that sent ripples through the internet, and just today hackers plastered pro‐Trump messages across Reddit.
  The public deserves to know about these kinds of stories, and I am oriented to tell them.
  This position with The Washington Post is a perfect blend of my technical skills, curiosity, and values.

  Thank you for your time and consideration, I will follow up by email in one weeks time.
  I look forward to discussing your Graphics Reporter role further.
\end{cvletter}
  % This is due to my strong visualization skill set from work through both internships and industry.
  % From classroom to career, I have a track record of distinguishing signal from noise.
  %
  % My senior year I enrolled in a Networking class, and investigated political tweets during the 2016 Presidential election.
  %   My work uncovered a network of fake accounts from over 1 TB of data, who were systematically pushing propaganda.